---
title: "The case for more GIS in front-line diplomacy"
output: html_notebook
---
|| [**0.0|READ ME**](#h_0.0_readme) || [1.0|EXTRACT](#h_1.0_extract) || [2.0|TRANSFORM](#h_2.0_transform) || [3.0|LOAD and ANALYSE](#h_3.0_analyse) || <br>

### 0.0 Read me {#h_0.0_readme}
> **Purpose of section**: brief outline of document, its content and pre-requisits<br>
> **Inputs**: none<br>
> **Outputs**: none

***

#### 0.1 Outline of document {#h_0.1_outline}
This notebook outlines the _process_ and _code_ outputs associated with a project on the role of GIS in international relations and diplomacy academia and practice.

**Final submission** and analysis can be found [here]() `13.01.2020`<br>


***


#### 0.2 Document index {#h_0.2_index}

0. [Read me]()
    + || [0.1-Outline](#h_0.1_outline) || [0.2-Index](#h_0.2_index) || [0.3-Setup](#h_0.3_prereq) ||
1. [Extract]()
    + || [1.1-Load](#h_1.1_load) || [1.2-Tidy](#h_1.2_tidy) || [1.3-Summarise](#h_1.3_summarise) ||
2. [Transform]()
    + || 0.1 || 0.2 || 0.3 || 0.4
3. [Load and analyse]()
    + || 0.1 || 0.2 || 0.3 || 0.4


***

#### 0.3 Pre-requisites and set up {#h_0.3_prereq}

In order for the code below to work, please ensure you have installed and loaded the relevant packages.

```{r}
#Installing packages (uncomment as required)
#install.packages(c("countrycode","tidyverse","sf","mapview","ggmap"))

library(countrycode) #iso tagging of countries
library(tidyverse) #number of packages for data manipulation, specifically want readr, dplyr, tibble
library(sf) #creation of spatial objects
library(mapview) #mapping package
library(ggmap) #for google api access 
```
<br>
Set parameters for the entire workflow
```{r}
#Set this to TRUE or FALSE to determine whether to use local, pre-loaded files or refresh via relevant API, i.e. (Google/ACLED) connections.
use_local_files <- TRUE
```

***

|| [0.0|READ ME](#h_0.0_readme) || [**1.0|EXTRACT**](#h_1.0_extract) || [2.0|TRANSFORM](#h_2.0_transform) || [3.0|LOAD and ANALYSE](#h_3.0_analyse) || <br>

### 1.0 Extract Lowy Institute data {#h_1.0_extract}
> **Purpose of section**: <br>
> **Inputs**: Local Lowy Institute dataset available [here](https://globaldiplomacyindex.lowyinstitute.org/about.html#){target="_blank"} <br>
> **Outputs**: Renamed and separated .csv filess

_**Note** on downloading from the Lowy Institute site, there may be incompatibility with downloads in Safari, chrome is recommended, have not tested other browsers._

***

#### 1.1 Load .csv file and check data types {#h_1.1_load}

```{r}
###Confirm working directory
print(getwd())

###open latest csv document based on relative path
lowy_raw_data <- read.csv("./Data/Raw_data/2019_LowyInstituteGlobalDiplomacyIndex_FullDataset.csv")
```

#### 1.2 Tidy up dataset {#h_1.2_tidy}
**Check for**: factors; rename columns; seperate out relevant columns <br>
**Output**: <br>

a. renamed data frame `lowy_renamed`
b. other meta data `lowy_meta`
c. ranking data `lowy_rank`
d. **posting data** `lowy_posting` **<===** this is the relevant one for the rest of the work

```{r}
###check for factor columns and change them to character columns
#more of a pre-emptive measure
i <- sapply(lowy_raw_data, is.factor)
lowy_raw_data[i] <- lapply(lowy_raw_data[i], as.character)

###column rename
#new data frame (a)
lowy_renamed <- lowy_raw_data

#rename columns
lowy_renamed <- lowy_renamed %>% dplyr::rename(
  send_country=COUNTRY,
  #metadata
  meta_gdp_usd_billions = GDP..B..USD.,
  meta_population_millions = POPULATION..M.,
  #ranking columns
  rank_g20 = G20.RANK,
  rank_OECD = OECD.RANK,
  rank_asia = ASIA.RANK,
  rank_overall = OVERALL.RANK,
  #post country info
  post_city = POST.CITY,
  post_country = POST.COUNTRY,
  post_type = TYPE.OF.POST,
  post_title = POST.TYPE.TITLE
  )

#data frame with all metadata (GDP and population) (b)
lowy_meta <- lowy_renamed[, c("send_country","meta_population_millions","meta_gdp_usd_billions")]

#data frame with all rankings (G20, OECD, Asia and overall) (c)
lowy_rank <- lowy_renamed[,c("send_country","rank_g20","rank_OECD","rank_asia","rank_overall")]

#data frame with information on sending country, post city, country as well as post type and title (d)
lowy_posting <- lowy_renamed[,c("send_country","post_city","post_country","post_type","post_title")]

###save data frames as .csv files ready for part 2
write.csv(lowy_posting,"./Data/Processing/Part_1_Out_Lowy_Posting.csv", row.names = FALSE)
write.csv(lowy_rank,"./Data/Processing/Part_1_Out_Lowy_Rank.csv", row.names = FALSE)
write.csv(lowy_meta,"./Data/Processing/Part_1_Out_Lowy_Meta.csv", row.names = FALSE)

#quick preview of data frame to work on
head(lowy_posting,2)
```

#### 1.3 Raw key information {#h_1.3_summarise}
Warning: an error may appear when running
```{r}
###report all unique values/entries
#Summarise all unique values in crude print out
for(column in colnames(lowy_posting)){
  cat(column,"has",length(apply(lowy_posting[column],2,unique)),"unique values\n")
}

###summary stats
lowy_type_table <- ftable(table(lowy_posting$send_country,lowy_posting$post_type))

###summarise count by send country
lowy_count_per_send_country <- lowy_posting %>% 
  group_by(send_country) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

per_country_count <- lowy_count_per_send_country$count

per_country_box <- boxplot(data=per_country_count, x=per_country_count, main="Diplomatic post count by sending country", 
   xlab="All post types", ylab="Count of posts",notch = TRUE)

cat("Per country count summary",
    "\nMin value:",per_country_box$stats[1,1],
    "\n25th percentile:",per_country_box$stats[2,1],
    "\nMedian value:",per_country_box$stats[3,1],
    "\n75th percentile:",per_country_box$stats[4,1],
    "\nMax value:",per_country_box$stats[5,1]
    )
###summarise count by post city
lowy_count_per_post_city <- lowy_posting %>% 
  group_by(post_city) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

per_post_city_count <- lowy_count_per_post_city$count

per_post_city_box <- boxplot(data=per_post_city_count, x=per_post_city_count, main="Diplomatic post count by post city ", 
   xlab="All post types", ylab="Count of posts",notch = TRUE)
cat("Per post city count summary",
    "\nMin value:",per_post_city_box$stats[1,1],
    "\n25th percentile:",per_post_city_box$stats[2,1],
    "\nMedian value:",per_post_city_box$stats[3,1],
    "\n75th percentile:",per_post_city_box$stats[4,1],
    "\nMax value:",per_post_city_box$stats[5,1]
    )
###summarise count by post country
lowy_count_per_post_country <- lowy_posting %>% 
  group_by(post_country) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

per_post_country_count <- lowy_count_per_post_country$count

per_post_country_box <- boxplot(data=per_post_country_count, x=per_post_country_count, main="Diplomatic post count by post country", 
   xlab="All post types", ylab="Count of posts",notch = TRUE)
cat("Per post country count summary",
    "\nMin value:",per_post_city_box$stats[1,1],
    "\n25th percentile:",per_post_city_box$stats[2,1],
    "\nMedian value:",per_post_city_box$stats[3,1],
    "\n75th percentile:",per_post_city_box$stats[4,1],
    "\nMax value:",per_post_city_box$stats[5,1]
    )
```

```{r include=FALSE}
###unload data frames from global environment that are not needed.
ls()
rm(list = ls()[grepl("box", ls())]) #remove all boxplots
rm(list = ls()[grepl("per", ls())]) #per counting dataframes
#rm(list = ls()) #purge all else (comment/uncomment as needed)
```


***

|| [0.0|READ ME](#h_0.0_readme) || [1.0|EXTRACT](#h_1.0_extract) || [**2.0|TRANSFORM**](#h_2.0_transform) || [3.0|LOAD and ANALYSE](#h_3.0_analyse) || <br>

### 2.0 Transform Lowy Institute data {#h_2.0_transform}
> **Purpose of section**: Load,.csv files; add country iso codes to main data frame; and geocode send country+post city+post+country+exact embassy location with Google API <br>
> **Inputs**: `Part_1_Out_Lowy_Posting.csv` from end of part 1<br>
> **Outputs**: `to be named` master geocoded table 

***

#### 2.1 Re-load {#h_2.1_load}
```{r}
lowy_data <- read_csv("./Data/Processing/Part_1_Out_Lowy_Posting.csv")
```

#### 2.2 ISO codes {#h_2.2_iso}
```{r}
###Set up

#iso dataframe
lowy_data_iso <- lowy_data

#country_iso list [column 1]
iso_list_send_country <- c()
iso_list_send_country_num <- c()
#post_country_iso list [column 3]
iso_list_post_country <- c()
iso_list_post_country_num <- c()

###ending country column (1) three digit numbers
for(country in lowy_data_iso[1]){
  country_iso <- countrycode(
    #call the entry of 'Country' for the row_number currently being taken by for loop
    sourcevar = country, 
    #three letter iso code
    destination = "iso3n",
    #based on english language names
    origin = "country.name")
  
  #add value to a list
  iso_list_send_country_num <- append(iso_list_send_country_num,country_iso)
}

###sending country column (1) three digit letters
for(country in lowy_data_iso[1]){
  country_iso <- countrycode(
    #call the entry of 'Country' for the row_number currently being taken by for loop
    sourcevar = country, 
    #three letter iso code
    destination = "genc3c", 
    #based on english language names
    origin = "country.name")
  
  #add value to a list
  iso_list_send_country <- append(iso_list_send_country,country_iso)
}
#===================================
###Post country column (3) three digit numbers
for(country in lowy_data_iso[3]){
  post_country_iso <- countrycode(
    #call the entry of 'Country' for the row_number currently being taken by for loop
    sourcevar = country, 
    #three letter iso code
    destination = "iso3n", 
    #based on english language names
    origin = "country.name")
  
  #add value to a list
  iso_list_post_country_num <- append(iso_list_post_country_num,post_country_iso)
}

###Post country column (3) three letters
for(country in lowy_data_iso[3]){
  post_country_iso <- countrycode(
    #call the entry of 'Country' for the row_number currently being taken by for loop
    sourcevar = country, 
    #three letter iso code
    destination = "genc3c", 
    #based on english language names
    origin = "country.name")
  
  #add value to a list
  iso_list_post_country <- append(iso_list_post_country,post_country_iso)
}

###create new columns
lowy_data_iso$send_country_iso = iso_list_send_country
lowy_data_iso$send_country_iso_num = iso_list_send_country_num

lowy_data_iso$post_country_iso = iso_list_post_country
lowy_data_iso$post_country_iso_num = iso_list_post_country_num

###preview data frame
head(lowy_data_iso,3)
```


#### 2.3 Geo-coding {#h_2.3_geocode}
This section requires a google api key; you can set one up [here](https://console.cloud.google.com/){target="_blank"} through the google cloud platform

```{r}
register_google(key = "AIzaSyDNlUg_mclZ4kSJMDvbj_UVMHds8vkz2nE")
```

Code to run the geocoding for each country column (`send_country` `post_country`), city `post_city` + `post country` (to avoid finding wrong city)

**Part 1 cities and countries**
```{r}
###========Preparation

###concatenate post city and post country columns
lowy_data_iso$post_city_country = paste(
  lowy_data_iso$post_city,
  lowy_data_iso$post_country,
  sep=", ")

###geo-c - concatenated city and country names
geo_city_country <- distinct(lowy_data_iso,post_city_country)
geo_city_country_df <- as.data.frame(geo_city_country)
#geo_city_country_df <- head(geo_city_country_df,4) #for sample work only

###geo-code - sending countries
geo_send_country <- distinct(lowy_data_iso,send_country)
geo_send_country_df <- as.data.frame(geo_send_country)
#geo_send_country_df <- head(geo_send_country_df,4) #for sample work only

###========POST CITIES
#if local file tag is set to TRUE, google api will not be used
if(use_local_files) {
  print("Local file flag set to TRUE, using local files")
  geo_city_country_df_dl <- read.csv("./Data/GoogleAPI/Geo_City_Country_DL.csv")
} else {
  print("Local file flag set to FALSE, calling google now!")
  geo_city_country_df_dl <- mutate_geocode(geo_city_country_df, post_city_country)
  #Save .csv file
  write.csv(geo_city_country_df_dl,"./Data/GoogleAPI/Geo_City_Country_DL.csv", row.names = FALSE)
}

###========SEND COUNTRIES
#if local file tag is set to TRUE, google api will not be used
if(use_local_files) {
  print("Local file flag set to TRUE, using local files")
  geo_send_country_df_dl <- read.csv("./Data/GoogleAPI/Geo_Send_Country_DL.csv")
} else {
  print("Local file flag set to FALSE, calling google now!")
  geo_city_country_df_dl <- mutate_geocode(geo_city_country_df, post_city_country)
  #Save .csv file
  write.csv(geo_send_country_df_dl,"./Data/GoogleAPI/Geo_Send_Country_DL.csv", row.names = FALSE)
}

###========VIEW DATAFRAMES
head(geo_city_country_df_dl,3)
head(geo_send_country_df_dl,3)

###========JOIN DATA TO MASTER DATA FRAME
lowy_data_geo <- lowy_data_iso

#Join send lon/lat
lowy_data_geo <- merge(lowy_data_geo,geo_send_country_df_dl, by = "send_country")

lowy_data_geo <- lowy_data_geo %>% rename(
  send_lon =lon,
  send_lat = lat)

head(lowy_data_geo)

#Join post city lon/lat
lowy_data_geo <- merge(lowy_data_geo,geo_city_country_df_dl, by = "post_city_country")

lowy_data_geo <- lowy_data_geo %>% rename(
  post_city_lon =lon,
  post_city_lat = lat)

head(lowy_data_geo)
```

**Part 2 exact embassy locations**<br>
Code to run the geocoding for exact embassy locations. Using combination of `send_country`+`post_country`+"Embassy"+ `post_city`
```{r}
###master dataframe with all data
lowy_data_geo_master <- lowy_data_geo

###Exact geocoding query
lowy_data_geo_master$full_geo_query = paste(
  lowy_data_geo_master$send_country,
  lowy_data_geo_master$post_title,
  lowy_data_geo_master$post_city_country,
  sep=", ")

###RUN GEOCODING
if(use_local_files) {
  print("Local file flag set to TRUE, using local files")
  lowy_data_geo_master <- read.csv("./Data/GoogleAPI/lowy_data_geo_master.csv")
} else {
  print("Local file flag set to FALSE, calling google now!")
  lowy_data_geo_master <- mutate_geocode(lowy_data_geo_master, full_geo_query)
  
  #rename columns
  lowy_data_geo_master <- lowy_data_geo_master %>% rename(
  exact_post_lon = lon,
  exact_post_lat = lat)
  
  #Save .csv file
  write.csv(geo_send_country_df_dl,"./Data/GoogleAPI/lowy_data_geo_master.csv", row.names = FALSE)
}

#Unload unnecessary data from global environment
rm(list = ls()) #purge all else (comment/uncomment as needed)

```

***

|| [0.0|READ ME](#h_0.0_readme) || [1.0|EXTRACT](#h_1.0_extract) || [2.0|TRANSFORM](#h_2.0_transform) || [**3.0|LOAD and ANALYSE**](#h_3.0_analyse) || <br>

### 3.0 Load and analyse Lowy Institute data {#h_3.0_analyse}
> **Purpose of section**: visualise coordinates; and run clustering analysis<br>
> **Inputs**: `lowy_data_geo_master` (final output of part 2)<br>
> **Outputs**: maps and visuals

***

#### 3.1 Load data and segmet usable part for analysis {#h_3.1_analysis_prep}
```{r}
###Load data from section 2
lowy_data_complete <- read_csv("./Data/GoogleAPI/lowy_data_geo_master.csv")

###Filter out unusable datapoints
#names(lowy_data_complete)

#Re-arrange columns and sort table
lowy_data_complete <-lowy_data_complete
lowy_data_complete = select(lowy_data_complete, 
                            #sending data
                            send_country_iso,
                            send_country,
                            send_lon,
                            send_lat,
                            #posting data
                            post_country_iso, 
                            post_country,
                            post_city_country,
                            post_city,
                            post_city_lon,
                            post_city_lat,
                            post_type,
                            post_title,
                            #other columns
                            everything())

lowy_data_complete <- lowy_data_complete[order(lowy_data_complete$send_country),]
head(lowy_data_complete)

#Filter out NA values (around 44 values)
geo_lowy_NA_values <- lowy_data_complete %>%
  dplyr::select(everything()) %>%
  dplyr::filter(is.na(exact_post_lon))

geo_lowy_no_NA <- lowy_data_complete %>%
  dplyr::select(everything()) %>%
  dplyr::filter(!is.na(exact_post_lon))

#Preview table
report_full_length <-length(lowy_data_complete$send_country)
report_na_length <- length(geo_lowy_NA_values$send_country)
report_non_na_length <- length(geo_lowy_no_NA$send_country)

cat("There are,", report_full_length,"entries in the complete data frame.","\nFrom these,",report_na_length,"are NA/blank. (",report_na_length/report_full_length*100,"% )","\nIn total,",report_non_na_length,"entries have valid coordinates.","\nTotal coverage is:",report_non_na_length/report_full_length*100,"%")


```


#### 3.2 Geo-coding analysis function {#h_3.2_geo_function}
Function to take in data frame, and a filter to visualise and return filtered dataframe for further analysis `f_exact_city_postings <- function(p_city_filter,p_df){}` see code [here](#ref_code) for further details
```{r include=FALSE}
###FUNCTION
f_exact_city_postings <- function(p_city_filter,p_df,p_colour = "red"){
  
  ###Subset of dataframe for chosen country
  sub_city_df <- p_df[p_df$post_city == p_city_filter,]

  #create spatial objects
  sub_city_sf <- 
    st_as_sf(sub_city_df,coords=c("post_city_lon","post_city_lat"),crs = 4326, remove = FALSE)

  sub_city_geo_sf <-
    st_as_sf(sub_city_df,coords=c("exact_post_lon","latexact_post_lat"),crs = 4326,remove = FALSE)

  #map view options
  mapviewOptions(leafletWidth = 750,leafletHeight = 400)
  
  #City lat longs
  exact_map <- mapview(
      #spatial object
      sub_city_sf,
      legend = FALSE,
      layer.name = "City coordinates",
      alpha.regions = 0.4,
      label = sub_city_df$post_city_country,
      cex = 10,
      popup = leafpop::popupTable(subset(sub_city_sf, select = c(post_city_country)))
      
      #Exact lat longs
      )+ mapview(
      #spatial object
      sub_city_geo_sf,
      legend = FALSE,
      layer.name = "Geocoded exact coordinates",
      label = sub_city_df$full_geo_query,
      color = p_colour,
      alpha.regions = 0.4,
      col.regions = p_colour,
      cex = 0.1,
      popup = leafpop::popupTable(subset(sub_city_sf, select = c(send_country_iso,send_country,post_type,post_title,exact_post_lon,latexact_post_lat)))
      )
  
  mapshot(exact_map, url = paste("/cloud/project/Data/MapFiles/",p_city_filter,"map.html",sep="_"))

  #return dl table,map
  return_list <- list(df = sub_city_df,map = exact_map)
  return(return_list)
}
```

#### 3.3 Visualise {#h_3.3_geo_vis}
Run function on array of cities of interest

```{r}
###run function
f_out <- f_exact_city_postings(p_city_filter = "Tehran",p_df = geo_lowy_no_NA)
f_out$map
```

#### 3.4 Clustering {#h_3.4_cluster}
Use function output from 3.3 to run DBSCAN spatial clustering analysis
```{r}

f_exact_city_cluster <- function(p_city_filter,p_df,p_eps,p_k = 4){
  #run original function
  f_out <- f_exact_city_postings(p_city_filter = p_city_filter,p_df = p_df)
  
  #assign coordinates of filtered dataset to variable
  db_coordinates <- f_out$df[14:15]
  
  #boxplot
  db_coordinates_box <- boxplot(data=db_coordinates$exact_post_lon, x=db_coordinates$exact_post_lon, main="Boxplot for coordinate values", 
   xlab="All post types", ylab="Count of posts",notch = TRUE) #[RETURN 1]
  
  #Indetify optimal eps 
  kNNdist_df <- dbscan::kNNdist(db_coordinates, k = p_k)
  db_kNN_plot <- dbscan::kNNdistplot(db_coordinates,k = p_k) #[RETURN 2]

  #now run the dbscan analysis
  db <- fpc::dbscan(db_coordinates, eps = p_eps, MinPts = p_k)
  
  #now plot the results [RETURN 3]
  db_plot <- plot(db, db_coordinates, main = "DBSCAN Output", frame = F)
  
  #add 1 to cluster to avoid 0 values as leaflet doesn't like to colour by 0 (zero) values
  f_out$df$cluster <- db$cluster+1
  dbscan_test_df <- f_out$df
  
  f_out_cluster <- f_exact_city_postings(p_city_filter = p_city_filter,p_df = dbscan_test_df,p_colour = dbscan_test_df$cluster)
  f_out_cluster$map #[RETURN 4]
  f_out_cluster$df #[RETURN 5]
  
  #return list of relevant elements
  return_list <- list(df_sub = f_out$df,map = f_out$map,box_plot = db_coordinates_box, k_plot = db_kNN_plot,f_cluster_map = f_out_cluster$map, f_cluster_df = f_out_cluster$df)
  return(return_list)
}

f_exact_city_cluster(p_city_filter = "London",p_df = geo_lowy_no_NA,p_eps = 0.02,p_k =4)


f_exact_city_cluster(p_city_filter = "Tehran",p_df = dbscan_test_df,p_colour = dbscan_test_df$cluster)

#extract coordinate columns
db_coordinates <- f_out$df[14:15]
#db_coordinates <- db_coordinates[order(db_coordinates$exact_post_lon),]

#boxplot to spot geographical outliers
db_coordinates_box <- boxplot(data=db_coordinates$exact_post_lon, x=db_coordinates$exact_post_lon, main="Boxplot for coordinate values", 
   xlab="All post types", ylab="Count of posts",notch = TRUE)

db_coordinates_box$out

#Remove geographical outliers
#db_coordinates <- db_coordinates[-(1:5),]

#Indetify optimal eps
kNNdist_df <- dbscan::kNNdist(db_coordinates, k = 2)
dbscan::kNNdistplot(db_coordinates,k = 2)

#now run the dbscan analysis
db <- fpc::dbscan(db_coordinates, eps = 0.017, MinPts = 2)
#now plot the results
plot(db, db_coordinates, main = "DBSCAN Output", frame = F)




f_out$df$cluster <- db$cluster+1
dbscan_test_df <- f_out$df

dbscan_test_df

f_out <- f_exact_city_postings(p_city_filter = "Tehran",p_df = dbscan_test_df,p_colour = dbscan_test_df$cluster)
f_out$map


```




#### REFERENCE CODE FUNCTIONS {#ref_code}

**`f_exact_city_postings()`**: 

```
###FUNCTION REFERENCE FOR CODE
###FUNCTION
f_exact_city_postings <- function(p_city_filter,p_df){
  
  ###Subset of dataframe for chosen country
  sub_city_df <- p_df[p_df$post_city == p_city_filter,]

  #create spatial objects
  sub_city_sf <- 
    st_as_sf(sub_city_df,coords=c("post_city_lon","post_city_lat"),crs = 4326)

  sub_city_geo_sf <-
    st_as_sf(sub_city_df,coords=c("exact_post_lon","exact_post_lat"),crs = 4326)

  #City lat longs
  exact_map <- mapview(
      #spatial object
      sub_city_sf,
      legend = FALSE,
      layer.name = "City coordinates",
      alpha.regions = 0.4,
      label = sub_city_sf$post_city_country,
      cex = 10
      
      #Exact lat longs
      )+ mapview(
      #spatial object
      sub_city_geo_sf,
      legend = FALSE,
      layer.name = "Geocoded exact coordinates",
      label = sub_city_geo_sf$full_geo_query,
      color = "red",
      alpha.regions = 0.4,
      col.regions = "red",
      cex = 0.1)
  
  mapshot(exact_map, url = paste("/cloud/project/Data/MapFiles/",p_city_filter,"map.html",sep="_"))

  #return dl table,map
  return_list <- list(df = sub_city_df,map = exact_map)
  return(return_list)
}
```



